---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CentralDogma

## Installation

You can install the development version of CentralDogma from [GitHub](https://github.com/) with:

``` r
# install.packages("CentralDogma")
CentralDogma::CentralDogma("rforbiodatascience24/group_03_package")
```

### Group members:

s225049: Ida Sofie Goldschmidt\
s225074: Annekatrine Kirketerp-Møller\
s225051: Emil August Dissing Berntsen\
s224974: Rasmus Kamp\
s215109: Rolf Larsen

### Loading the library

```{r setup}
library(CentralDogma)
```

## Description

### sample_nuc

***sample_nuc*** takes an integer as input and outputs a string. The output string is a DNA sequence, which is a character-string only using "A", "C", "T" and "G" representing each of the nucleotides in DNA. The length of the string is based on the input integer.

### find_stop_start

The **find_stop_start** function takes on a string of amino acids and finds possible start and stop codons index positions in that string. 

### translate_DNA

***translate_DNA*** takes a DNA string as input and outputs the corresponding RNA string. The input string is translated by replacing every "T" with a "U". The input could for example come from the output from ***sample_nuc()***.

### Extract_codons

The **extract_codons** function takes in two parameters, where the first is the RNA-sequence and the second parameter is the start, from there the function will start reading (where if no start is specified, default is 1). The function then extracts consecutive three-character codons, and lastly It returns a vector of codons, useful for sequence analysis tasks.

### transscript_aa_sequence

This code takes a vector made up of RNA codons in pairs of three RNA nucleotides, and transscripts them into a string of amino acids representen by their single letter code.

### plot_aas

The **plot_aas** function takes an string of amino acids in their single letter format. It then splits that string into a single character vector, and counts the number of occurrences of each amino acid, resulting in the creating of a dataframe. It then plots the data frame in a column plot with the x-axis being the amino acids and the y-axis being their counts.

## Demonstration

An example of a string with the length 60, created using *sample_nuc()* is shown below.

```{r}
set.seed(5)
dna <- sample_nuc(60)
dna
```

An example of the use of *translate_DNA* can be seen below:

```{r}
rna <- translate_DNA(dna)
rna
```

An example of the start and stop codons function:

```{r}
codon_index <- find_stop_start(dna)
print(codon_index)
```

An example of how the extract_codons functions can be used

```{r}
codons <- extract_codons(rna, 1)
codons
```

An example of the transcription function:

```{r}
trans <- transscript_aa_sequence(codons)
trans
```

An example of the plot function:

```{r}
plot_aas(trans)
```

## Discussion

This package can be useful when working with DNA-sequences, since the most basic functions are created. The package can translate and transcribe a given DNA string, find codons as well as create sample-strings used for testing if no real data is available. The package can also plot the amounts of each amino acid in a amino acid sequence, which can be useful to give an overview of the sequence, and to determine whether any amino acids seem particularly abundant in the sequence.

Further functions could be to determine characteristics of the amino acids, for example if they are acidic, basic, hydrophobic, hydrophilic or have other chemical properties. This information could also be plotted to show the chemical properties of a string. \
Another function could be to determine reading frames, to find the coding region. This could also be used to find specific parts in the non-coding regions like the promoter region or the TATA-box. These parts are not entirely conserved, so the results might not be definitive, but could give probabilities for where the regions are placed.
