---
title: "CentralDogma"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{CentralDogma}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(CentralDogma)
```

## Description

### sample_nuc

*sample_nuc* takes an integer as input and outputs a string. The output string is a DNA sequence, which is a character-string only using "A", "C", "T" and "G" representing each of the nucleotides in DNA. The length of the string is based on the input integer.

### translate_DNA

*translate_DNA* takes a DNA string as input and outputs the corresponding RNA string. The input string is translated by replacing every "T" with a "U". The input could for example come from the output from *sample_nuc()*,

## Demonstration

An example of a string with the length 6, created using *sample_nuc()* is shown below.

```{r}
set.seed(3)
dna <- sample_nuc(6)
dna
```

An example of the use of *translate_DNA* can be seen below:

```{r}
rna <- translate_DNA(dna)
rna
```

## Discussion
